Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-18 Manuscript/FLPhish(Trans).tex
修改语法和用词不当错误

\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data. Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using their gradient model updates. In each iteration of FL, the central server sends a model to each client. The client uses its own private data to update the model and sends the model gradient update back to the central server. Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model. Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.

\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system. On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}. On the other hand, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}. And such attacks are referred as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks for some designed attacks can still bypass the defense \cite{ref_06_model}. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by supporting different types of deep learning models in each client and makes FL more flexible.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}

@@

\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected. Median sorts the values of each parameter of all local model updates as well. Besides it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

@@

\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a groups of FL clients.
  \begin{figure}
    \centering
  \includegraphics[width=0.5\textwidth]{figures/Figure_System.pdf}
  \caption{System Model\&Threat Model.}
  \label{fig_system}
  \end{figure}   
\subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each iteration. After receiving the gradient updates from all the clients, the FL server aggregates the gradient updates for a global update based on FedAvg. After the aggregation process, the FL server updates the global model.

@@

\subsection{Threat Model}
The current system suffers from the Byzantine attacks. Malicious Byzantine client $c_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $c_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}. Byzantine client $c_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $c_{i}$ dispatches the false model gradient updates to the central server. Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

@@

\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication cost. Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in a long term. Therefore, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation. Furthermore, we propose two aggregation rules in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

@@

\section{Proposed FLPhish Scheme}
In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning, the phishing mechanism, the reputation mechanism, and the aggregation rules.

\begin{algorithm}[t]
  \caption{Ensemble FL} %algorithm name
  \label{alg:system}
  \hspace*{0.02in} {\bf Input:} %the input of the algorithm
  the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$; number of training iterations $T$; unlabeled batch size $n$;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its own local dataset $d_i$;
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ samples) from $D$;
      \For{\textit{i=1,2,3,...,u}}
        \State $s \overset{D_{t}}{\rightarrow} c_{i}$;
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$;
        \State $c_i \overset{\mathbf{k_i^t}}{\rightarrow} s$;
      \EndFor
      \State $Y_t$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$;
      \State $\mathbf{M}$ = $ModelUpdate(Y_t, D_t, \mathbf{M})$;
    \EndFor \\
    \Return $\mathbf{M}$.
  \end{algorithmic}
\end{algorithm}
\begin{algorithm}[t]
  \caption{KnowledgeEnsemble} %algorithm name
  \label{alg:KnowledgeEnsemble}
  \hspace*{0.02in} {\bf Input:} %input of the algorithm
  the ensemble of ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th procedure; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
      \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
      \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
    \EndFor \\
    \Return $\mathbf{\hat{y}^t}$.
  \end{algorithmic}

@@

\subsection{Designed Ensemble Federated Learning}
Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
\par Unlike existing FL architecture, which adopts clients' model gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.
\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc. The collected data is labeled and preprocessed by {$c_{i}$}, and {$c_{i}$} adopts the preprocessed local dataset to train its local model. When receiving a public dataset from the central server, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
\subsubsection{{Central server}} The central server {$s$} is responsible for making a public dataset and building a global model. The public dataset consists of a variety of unlabeled data whose labels are not possessed by the central server. The public dataset is collected by {$s$} or produced by it (such as using GAN to generate data). After the construction of the public dataset, {$s$} sends the public dataset to the clients. Each client {$c_{i}$} sends its predictions of the public dataset back to {$s$}. After receiving all the predictions, {$s$} aggregates the predictions for an aggregated predictions. Then {$s$} employs the aggregated predictions and the public dataset to train the global model.

@@

  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL. Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients) instead of model gradient updates as the aggregation substances. Different selected features in different clients are permitted as well.
  \item The overhead and latency of the communication process are significantly reduced in comparison with the typical FL architecture. Transferring data is much faster than transferring gradient updates due to the smaller size. 
  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof is in the section IV.B.
\end{itemize}

\subsection{Phishing Mechanism-based Detection}
The proposed Ensemble FL still confronts the threat of Byzantine attacks. Malicious clients can manipulate their local model via label flipping. They mislabel the local dataset to build a `poisoned' local model. When malicious clients receive unlabeled data from the central server, they manufacture false predictions (called poisoned knowledge) and send these false predictions to the central server. Subsequently, the central server aggregates the false predictions as the labels of the unlabeled dataset. Then central server trains the global model using these unlabeled datasets with the false aggregation predictions. Therefore, a flawed global model is produced. Inspired by the idea of ensemble learning, we consider utilizing the labeled data in the architecture of Ensemble FL to cope with Byzantine attacks. We called labeled data `bait'.
  \par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$. Each client $c_i$ possesses a local dataset $d_i$. At the beginning of the Ensemble FL, $c_{i}$ utilizes its local dataset $d_i$ to train a local model $\mathbf{m_i}$ as
  \begin{equation}
    \mathbf{m_i}=Train(d_i).
  \end{equation}
  \par Step-2: \ul{\textit{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly. Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
  \begin{equation}
    s \overset{{D_{t},B_{t}}}{\rightarrow} c_{i}.
  \end{equation}
  \par Step-3: \ul{\textit{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
  \begin{equation}
    \mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i})
  \end{equation}
  ($c_i$ can not distinguish between $D_t$ and $B_t$) via the local model trained by itself in Step 1  and sends its prediction back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix}.
  \end{equation}

>>>>

\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data. Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using their gradient model updates. In each iteration of FL, the central server sends a model to each client. The client uses its private data to update the model and sends the model gradient update back to the central server. Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model. Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.

\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system. On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}. On the other hand, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}. And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregation process. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks for some designed attacks can still bypass the defense \cite{ref_06_model}. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}

@@

\subsection{Byzantine Defense Methods in Federated Learning}
Byzantine-robust schemes are very important for FL to enhance its security as Byzantine attacks can cause great damages to the FL system. Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al.} developed an approach called Krum, which selects one client's update as a global model based on a square-distance score in each iteration \cite{ref_12_defense}.
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation rules called Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected, and cuts off the largest ones and the smallest ones. Median sorts the values of each parameter of all local model updates as well. Besides it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach called DRACO to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Xie \textit{et al.} proposed Zeno, which uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

@@

\subsection{System Model}We first show the system architecture of a typical FL with two entities, FL server, and a group of FL clients.
  \begin{figure}
    \centering
  \includegraphics[width=0.5\textwidth]{figures/Figure_System.pdf}
  \caption{System Model\&Threat Model.}
  \label{fig_system}
  \end{figure}   
\subsubsection{{FL Server}} FL server $s$ sends a global model to each client at each iteration. After receiving the gradient updates from all the clients, the FL server aggregates the gradient updates for a global update based on FedAvg. After the aggregation process, the FL server updates the global model.

@@

\subsection{Threat Model}
The current system suffers from the Byzantine attacks. Malicious Byzantine client $b_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $b_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}. Byzantine client $b_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server. Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

@@

\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and introducing high communication costs. Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
\par \textit{3)} As the performance of each client remains not stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in the long term. Therefore, we further propose an effective Bayesian inference-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation. Furthermore, we propose two aggregation rules in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

@@

\section{Proposed FLPhish Scheme}
In this section, we show the proposed FLPhish scheme including the Ensemble Federated Learning architecture, the phishing mechanism, the reputation mechanism, and the aggregation rules.

\begin{algorithm}[t]
  \caption{Ensemble FL} %algorithm name
  \label{alg:system}
  \hspace*{0.02in} {\bf Input:} %the input of the algorithm
  the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$; number of training iterations $T$; unlabeled batch size $n$;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$;
    \For{\textit{t=1,2,3,..,,T}}
      \State $s$ selects $D_t$ (containing $n$ samples) from $D$;
      \For{\textit{i=1,2,3,...,u}}
        \State $s \overset{D_{t}}{\rightarrow} c_{i}$;
        \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$;
        \State $c_i \overset{\mathbf{k_i^t}}{\rightarrow} s$;
      \EndFor
      \State $Y_t$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$;
      \State $\mathbf{M}$ = $ModelUpdate(Y_t, D_t, \mathbf{M})$;
    \EndFor \\
    \Return $\mathbf{M}$.
  \end{algorithmic}
\end{algorithm}
\begin{algorithm}[t]
  \caption{KnowledgeEnsemble} %algorithm name
  \label{alg:KnowledgeEnsemble}
  \hspace*{0.02in} {\bf Input:} %input of the algorithm
  the ensemble of ${\mathbf{k_i^t}}_{\left \{ i= 1,2,3,...,u \right \}}$; size of each client's local dataset ${e_i}_{\left \{ i= 1,2,3,...,u \right \}}$; the unlabeled dataset $D_t$ used in $t$th procedure; $\mathbf{\hat{y}^t}$ is the ensembled prediction of dataset $D_t$; $\mathbf{\hat{y}^t_l}$ denotes the prediction of the dataset $D_t$ made by $i$th client;\\
  \hspace*{0.02in} {\bf Output:} %output of the algorithm
  \begin{algorithmic}[1]
    \For{$l=1,2,3,...,n$ ($l=1,2,3,...,n$, denotes the data point in the unlabeled dataset)}
      \State $\mathbf{\hat{k}^t}$ $\gets$ $\sum_{i=1}^{u}\frac{e_i}{\sum_{i=1}^{u}e_i}\mathbf{\hat{k}^t}_i$;
      \State $\mathbf{\hat{y}^t}\gets argmax(\mathbf{\hat{k}^t})$;
    \EndFor \\
    \Return $\mathbf{\hat{y}^t}$.
  \end{algorithmic}

@@

\subsection{Designed Ensemble Federated Learning}
Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
\par Unlike existing FL architecture, which adopts clients' model gradient updates for global model updates, we apply an unlabeled dataset preserved by the central server and the clients' predictions of it for global aggregation.
\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc. The collected data is labeled and preprocessed by {$c_{i}$}, and {$c_{i}$} adopts the preprocessed local dataset to train its local model. When receiving a public dataset from the central server, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
\subsubsection{{Central server}} The central server {$s$} is responsible for making a public dataset and building a global model. The public dataset consists of a variety of unlabeled data whose labels are not possessed by the central server. The public dataset is collected by {$s$} or produced by it (such as using GAN to generate data). After the construction of the public dataset, {$s$} sends the public dataset to the clients. Each client {$c_{i}$} sends its predictions of the public dataset back to {$s$}. After receiving all the predictions, {$s$} aggregates the predictions for the aggregated predictions. Then {$s$} employs the aggregated predictions and the public dataset to train the global model.

@@

  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL. Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients) instead of model gradient updates as the aggregation substances. Different selected features in different clients are permitted as well.
  \item The overhead and latency of the communication process are significantly reduced in comparison with the typical FL architecture. Transferring data and labels is much faster than transferring models and model gradient updates due to the smaller size of data and labels. 
  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof is in the section IV.B.
\end{itemize}

\subsection{Phishing Mechanism-based Detection}
The proposed Ensemble FL still confronts the threat of Byzantine attacks. Malicious clients can manipulate their local model via label flipping. They mislabel the local dataset to build a `poisoned' local model. When malicious clients receive unlabeled data from the central server, they manufacture false predictions (called poisoned knowledge) and send these false predictions to the central server. Subsequently, the central server aggregates the false predictions as the labels of the unlabeled dataset. Then the central server trains the global model using these unlabeled datasets with the false aggregation predictions. Therefore, a flawed global model is produced. Inspired by the idea of ensemble learning, we consider utilizing the labeled data in the architecture of Ensemble FL to cope with Byzantine attacks. We called labeled data `bait'.
  \par Step-1: \ul{\textit{Local Model Training}} The ensemble of clients $C=\left \{ c_{1},c_{2},...,c_{n-1},c_{n} \right \}$. Each client $c_i$ possesses a local dataset $d_i$. At the beginning of the Ensemble FL, $c_{i}$ utilizes its local dataset $d_i$ to train a local model $\mathbf{m_i}$ as
  \begin{equation}
    \mathbf{m_i}=Train(d_i).
  \end{equation}
  \par Step-2: \ul{\textit{Dataset Transferring}} Central server $s$ selects $n$ samples of data $D_t$ from unlabeled dataset $D$ and $m$ samples of data $B_t$ from labeled dataset $B$ randomly. Then $s$ sends $D_t$ and $B_t$ to each client $c_i$ as
  \begin{equation}
    s \overset{{D_{t},B_{t}}}{\rightarrow} c_{i}.
  \end{equation}
  \par Step-3: \ul{\textit{Label Predicting}} Each client $c_i$ predicts the labels of the unlabeled data $D_t$ and the labeled data $B_t$:
  \begin{equation}
    \mathbf{k_i^t}=Predict(D_t, B_t, \mathbf{m_i})
  \end{equation}
  ($c_i$ can not distinguish between $D_t$ and $B_t$) via the local model trained by itself in Step 1  and sends its prediction back to the central server as the distilled knowledge $\mathbf{k_i^t}$:
  \begin{equation}
    \mathbf{k_i^t}=\begin{vmatrix}
      p_{1,1} & p_{1,2} & \cdots  & p_{1,g-1} & p_{1,g}\\ 
      \vdots  & \vdots & \ddots  & \vdots & \vdots\\ 
      p_{n,1} & p_{n,2} & \cdots  & p_{n,g-1} & p_{n,g}
      \end{vmatrix}.
  \end{equation}

  \begin{algorithm}[t]
    \caption{Phishing Mechanism} 
    \hspace*{0.02in} {\bf Input:} 
    the ensemble of clients $C$ with local dataset $d_i$, $i=1,2,3,...,u$; a central server $s$ with unlabeled dataset $D$ and labeled dataset $B$; number of training iterations $T$; unlabeled batch size $n$;labeled batch size $m$.\\
    \hspace*{0.02in} {\bf Output:} 
    output result
    \begin{algorithmic}[1]
      \State $\mathbf{m_i}$ $\gets$ each client $c_i$ train a local model using its local dataset $d_i$.
      \For{\textit{t=1,2,3,..,,T}}
        \State $s$ selects $D_t$ (containing $n$ samples) from $D$ and $B_t$ (containing $m$ samples) from $B$.
        \For{\textit{i=1,2,3,...,u}}
          \State $s$ sends $D_t$ and $B_t$ to $c_i$.
          \State $c_i$ makes predictions $\mathbf{k_i^t}$ of the $D_t$ and $B_t$.
          \State $c_i$ sends $\mathbf{k_i^t}$ to $s$.
          \State $s$ calculates the accuracy $a_i^t$ of the predictions of $B_t$ made by $c_i$ in $t$th procedure.
          \If{$a_i^t > r_q$}
            \State $q_i = 1$.
            \For{\textit{j=i,i+1,i+2,...,u-1}}
              \State $(d,c,\mathbf{k^t},q,a^t)_j \gets (d,c,\mathbf{k^t},q,a^t)_{j-1}$.
            \EndFor
          \EndIf
        \EndFor
        \State $\mathbf{K_t}$ = $KnowledgeEnsemble(\mathbf{k_1^t},\mathbf{k_2^t},\mathbf{k_3^t},...,\mathbf{k_u^t})$.
        \State $\mathbf{M}$ = $ModelUpdate(\mathbf{K_t}, D_t, \mathbf{M})$.
      \EndFor
      \State\Return $\mathbf{M}$
    \end{algorithmic}
    \end{algorithm}
